---
title: "ling_tax_example"
author: "C. Weber"
date: "2025-09-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Syntax

Course numbers are identified as combinations of letters and numbers with no spaces in between.  The number and order of letters and numbers in a course number varies between universities but for my project they all consist of some combination of capital letters followed by some combination of numbers and possibly letters.

Quotes identify a chunk of information for the code to do something with.  If a course is required and there’s nothing else to consider, then it will be represented as “CHEM101”.  
**Instructions to code: weigh based on the number of credits assigned to that course.**

If a course is identified as having more than one possible number of credits, the max_credits field will be "1-4 credits," for example. 
**Instructions to code: I am not sure what to do here - something to do with listing all possible versions of the course: one version with 1 credit, one version with 2 credits, etc etc** 

**Combinations of course sequences** and **lists of courses that the student must choose from** will also be enclosed in quotes - the course numbers can still be identified within those quotes by looking for discrete combinations of letters and numbers. 

## Scenarios to code

A course is required, no options, will be represented like this:
"CHEM101"
**Instructions to code: weigh the course based on the number of credits assigned to it.**

If students must choose a single course from a list of possible courses, this is an “or” situation and represented by a pipe |, like this: 
“CHEM101|PHYS101|MATH302”
**Instructions to code: weigh each course based on the number of credits assigned to it, then weigh by 1 over the number of courses in the list.**

If students must take a set sequence of courses (usually a two course lecture/lab combo), this is represented using the ampersand & surrounded by spaces, like this: 
“CHEM101 & CHEZ101”
**Instructions to code: weigh the sequence based on the sum of the credits assigned to each course.**

The “or” and “and” can be used in combination, if a student can choose between different multi-course sequences: 
“CHEM101 & CHEZ101|PHYS101 & PHYZ101”
**Instructions to code: weigh each sequence based on the summed number of credits assigned to each course in it, then weigh by 1 over the number of sequences in the list.**

There can be combinations of single courses and multi-course sequences within a list of courses to choose from, examples: 

Select one course sequence from the following:   
- CLSE 101.  
- EGRB 102 & EGRB 104.  
- EGRB 101.  
- EGMN 103 & EGMN190.  

Would be represented as : 
"CLSE101|EGRB102 & EGRB104|EGRE101|EGMN103 & EGMN190"

Choose one of the following options:   
- Option A : CHEM 101 and CHEZ 101.  
- Option B: PHYS 207.  
- Option C: BIOL 151 and BIOZ 151.  

Would be represented as: 
“CHEM101 & CHEZ101|PHYS207|BIOL151 & BIOZ151”
**Instructions to code: the single courses get a weight based on their assigned credits, the sequences get a weight based on the summed credits for all courses in the sequence, then each of those is divided by 1 over the number of weights in the group (which is a combination of both single courses and multi-course sequences).**

If students must choose a set number of courses, like “pick 3 courses,” from a list of courses or course sequences, then each course or course sequence is separated by the number of courses that must be chosen enclosed in square brackets, like this: 

“CHEM101[3]CHEM102[3]PHYS101[3]MATH402[3]ENGL101”

**Instructions to code: weigh each course or course sequence based on the assigned number of credits, then find all possible combinations of 3 courses without repeating and the weights of each combination, then weigh the total by 1 over the number of possible combinations that there are.**

If students must select a set number of credits from a list of courses or course sequences, then each course or course sequence is separated by the number of credits that must be chosen plus the letters “cred” enclosed in square brackets, like this:
“CHEM101[6cred]CHEM102[6cred]PHYS101[6cred]MATH402[6cred]ENGL101”
**Instructions to code: weigh each course or course sequence based on the assigned number of credits, then find all possible combinations that get you to 6 credits without repeating and along with the summed weights of each combination, then weigh the total by 1 over the number of possible combinations that there are.**


```{r}
#| warnings: false
#| messages: false
suppressPackageStartupMessages(library(tidyverse))

# List of courses with their assigned number of credits and course descriptions to be used as an example.
example_courses <- read.csv("example_courses.csv")

# Three examples of programs and their required courses, using hte syntax described above.
example_program_1 <- c("MATH151","PHYS201|PHYS207","BIOL152 & BIOL317","ENVS330|ENVS101 & ENVS102|ENVS343","CHEM101[3]CHEZ101[3]MATH151[3]ENVS401","URSP204[9cred]CHEM102[9cred]ENVS105[9cred]ECON325[9cred]ENVS321")
example_program_2 <- c("BIOL2100|BIOL2200","CHEM1410","CHEM1411","PHYS1425","PHYS1429","MATH1310","MATH1220|MATH1320","EVSC2801","EVSC2800","EVSC2801","EVSC3200","EVSC3201","EVSC3300","EVSC3301","EVSC3600","EVSC3601")
example_program_3 <- c("BIOL212","BIOL212L","CHEM103|CHEM121","CHEM111L","ECON203","EVST220","IDST490","LDSP250","MATH125","ENGL393","PHIL376","POLS371W","ANTH325[4]SOCL325[4]ANTH331[4]CHEM103[4]CHEM104[4]CHEM104L[4]ECON301[4]EVST395[4]EVST495[4]GEOG308[4]HIST342[4]HIST343[4]POLS391[4]RSTD337[4]RSTD338")
```




